Distributed multi-objective evolutionary optimization using island-based selective operator application

### 2019-02-13 hpmoon-asoco.tex
Some suggestions for captions @fergunet

\end{tabular}
}
\caption{Average quality metrics obtained after 30 runs per configuration, for the 4 methods compared: baseline (B), disjoint (D), overlapped (O) and \textcolor{blue}{automatic} overlapped (A), using a chromosome length of 512 dimensions. Acronyms next to values indicate that there is not significant difference with respect to that method for that value. Best values are marked in bold. Equiv-$X$ implies that value is the same as executing $X$, since both configurations would be the same.}
\label{tab:results512}
\end{table*}

>>>>

\end{tabular}
}
\caption{Average quality metrics obtained after 30 runs per
  configuration, for the 4 methods compared: baseline (B), disjoint
  (D), overlapped (O) and \textcolor{blue}{automatic} overlapped
  (A), % No sería mejor "automatically overlapped" or "automatic
       % overlap"? This does not sound good - JJ
  using a chromosome length of 512 dimensions. Acronyms next to values
  indicate that there is not significant difference with respect to
  that method for that value. Best values are marked in
  bold. Equiv-$X$ implies that value is the same as executing $X$,
  since both configurations would be the same.}  
\label{tab:results512}
\end{table*}
